### 2020-04-25 README.Rmd
draft: corrplot and docum

This is a list of U.S. datasets that can be accessed directly or in a `tibble` containing also COVID-19 metrics:

@@

This is a list of Italy datasets that can be accessed directly or in a `tibble` containing also COVID-19 metrics:

>>>>

This is a list of U.S. datasets that can be accessed directly or in a `dataframe` containing also COVID-19 metrics:

@@

This is a list of Italy datasets that can be accessed directly or in a `dataframe` containing also COVID-19 metrics:
